Project Examples

### 2023-05-13 Project Examples/Programs/project_examples.Rmd
Add non-shiny example

---
title: "Project Examples"
output: html_document
date: "2023-05-01"
runtime: shiny
---

@@

```{r school_table}
radioButtons("district", "Data for which District?", unique(data$district))

renderTable({
  data %>%
    filter(district == input$district) %>%
    mutate(across(ends_with("Rate"), ~ . * 100))
})
```

@@

```{r visualization, fig.dim=c(10, 8)}

>>>>

---
title: "Project Examples"
output: html_document
date: "2023-05-01"
---

@@

@@

```{r bargraph, fig.dim=c(10, 8)}

data_dist %>%
  rename_with(~ str_to_title(gsub("(Total)(\\w+)(Response)(Rate)_(\\w+)$", "\\1 \\2 \\3 \\4 \\5", .x, perl = T)), starts_with("Total")) %>%
  select(District, `Total Student Response Rate Mean`) %>%
  ggplot(aes(x = District, y = `Total Student Response Rate Mean`*100, fill = District, label = round(`Total Student Response Rate Mean`*100, 2))) +
  geom_bar(stat = "identity") +
  geom_text(vjust= -.5) +
  scale_y_continuous(limits = c(0, 100)) +
  ggtitle("Mean Student Response Rate by District") +
  ylab("Response Rate") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

```{r heatmap, fig.dim=c(10, 8)}
